Box 1 - TDT Curves

### 2023-09-19 ms/ms.qmd
MOved docs to folder to clean up

---
title: ""
author: et al. 
date: "`r Sys.Date()`"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: ./bib/template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable,  patchwork, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, bayesplot)

@@

```{r, tree}
# Bring in the fly tree
  tree <- read.tree("./phylogeny/drosi2.tre")

@@

# Grab out data
   data <- read.csv("./data/drosi_data.csv")

# functions
  source("./R/func.R")
  t <- tree_checks(tree2, data = data, dataCol = "species", type = "check")
  data <- data %>% mutate(species = gsub(" ", "", species),
                          phylo = species,
                          obs = 1:n()) %>% filter(!species %in% t$Species_InData_But_NotTree) 
  tree3 <- tree_checks(tree2, data = data, dataCol = "species", type = "prune")
  tree_checks(tree3, data = data, dataCol = "species", type = "check")

@@

  saveRDS(mcmcglmm_model, file = "./output/model/mcmcglmm_model")
  saveRDS(mcmcglmm_model_z_trans, file = "./output/model/mcmcglmm_model_z_trans")
  saveRDS(mcmcglmm_model_z_trans_nophylo, file = "./output/model/mcmcglmm_model_z_trans_nophylo")
} else{
                mcmcglmm_model <- readRDS("./output/model/mcmcglmm_model")
        mcmcglmm_model_z_trans <- readRDS("./output/model/mcmcglmm_model_z_trans")
mcmcglmm_model_z_trans_nophylo <- readRDS("./output/model/mcmcglmm_model_z_trans_nophylo")
}

>>>>

---
title: "Box 1 - TDT Curves"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable,  patchwork, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, bayesplot, here)

@@

```{r, tree}
# Bring in the fly tree
  tree <- read.tree(here::here("phylogeny/", "drosi2.tre"))

@@

# Grab out data
   data <- read.csv(here::here("data", "drosi_data.csv"))

# functions
  source(here::here("R", "func.R"))
  t <- tree_checks(tree2, data = data, dataCol = "species", type = "check")
  data <- data %>% mutate(species = gsub(" ", "", species),
                          phylo = species,
                          obs = 1:n()) %>% filter(!species %in% t$Species_InData_But_NotTree) 
  tree3 <- tree_checks(tree2, data = data, dataCol = "species", type = "prune")
  tree_checks(tree3, data = data, dataCol = "species", type = "check")

@@

  saveRDS(mcmcglmm_model, file =  here::here("output/model", "mcmcglmm_model"))
  saveRDS(mcmcglmm_model_z_trans, file = here::here("output/model", "mcmcglmm_model_z_trans")) 
  saveRDS(mcmcglmm_model_z_trans_nophylo, file =  here::here("output/model", "mcmcglmm_model_z_trans_nophylo")) 
} else{
                mcmcglmm_model <- readRDS(here::here("output/model/", "mcmcglmm_model"))
        mcmcglmm_model_z_trans <- readRDS(here::here("output/model/", "mcmcglmm_model_z_trans"))
mcmcglmm_model_z_trans_nophylo <- readRDS(here::here("output/model/", "mcmcglmm_model_z_trans_nophylo"))
}
